---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document: 
    keep_md: true
---

### Loading and preprocessing the data
The following code reads in the activity data file and converts the date field.

Afterwards it produces a summary and computes the mean steps per day.
```{r}
temp <- tempfile()
download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
activity <- read.csv(unz(temp, "activity.csv"))
str(activity)
activity$date<-as.Date(activity$date,"%Y-%m-%d")
summary(activity)
Tage <-aggregate(activity$steps, by=list(Date=activity$date), FUN="sum", na.rm=TRUE)
meansteps<-mean(Tage$x, na.rm = T)
```

### What is mean total number of steps taken per day?

The mean number of steps per day is `r meansteps`.

```{r, echo=FALSE}
par(mfrow=c(1,1))
with(Tage,{
  plot(Date,x,type="l",ylab="steps",xlab="date")})

par(mfrow=c(1,1))
with(Tage,{
  hist(x,col='red', main="steps taken per day",xlab="steps taken per day")})
```

### What is the average daily activity pattern?
```{r  }
Minuten <-aggregate(activity$steps, by=list(Date=activity$interval), FUN="mean", na.rm=TRUE)

par(mfrow=c(1,1))
with(Minuten,{
  plot(Date,x,type="l",ylab="steps",xlab="date")})
```


### Imputing missing values

 Get the location of the NA values.
```{r  }
nanew <-aggregate(activity$steps, by=list(Date=activity$interval), FUN="median", na.rm=TRUE)
naindex <- which(is.na(activity$steps)==TRUE)
#activity$steps[naindex,1] <- nanew$x[naindex]
```

### Are there differences in activity patterns between weekdays and weekends?
```{r, echo=F  }
Sys.setlocale("LC_TIME", "English")
weekend <- weekdays(as.Date(activity$date)) %in% c("Saturday", "Sunday") 
activity$daytype[weekend == TRUE] <- "weekend" 
activity$daytype[weekend == F] <- "weekday"


weekendsteps <-aggregate(activity$steps[activity$daytype=="weekend"], by=list(Date=activity$interval[activity$daytype=="weekend"]), FUN="mean", na.rm=TRUE)
weekdaysteps <-aggregate(activity$steps[activity$daytype=="weekday"], by=list(Date=activity$interval[activity$daytype=="weekday"]), FUN="mean", na.rm=TRUE)
steps<-cbind(weekendsteps,weekdaysteps)
colnames(steps)[4]<-"weekdaysteps"
colnames(steps)[2]<-"weekendsteps"
par(mfrow=c(2,1),mar=c(1, 1,1, 1))
with(steps,{
  plot(Date,weekdaysteps,type="l",ylab="Weekday steps")
  plot(Date,weekendsteps,type="l",ylab="Weekday steps",xlab="Interval")
  })

```

